%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.11 (19/6/14)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------

\documentclass[11pt,letterpaper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{black} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage[scale=0.75]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------

\firstname{Jim} % Your first name
\familyname{Notwell} % Your last name

% All information in this block is optional, comment out any lines you don't need
% \title{Curriculum Vitae}
\address{640 Coleman Ave, Apt 5}{Menlo Park, CA 94025}
\mobile{(+1) 614 403 1661}
\email{jimnotwell@gmail.com}
%\homepage{https://www.linkedin.com/pub/daniele-perrotta/64/5b9/794} {staff.org.edu/$\sim$jsmith} % The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example
%\extrainfo{additional information}
%\quote{"A witty and playful quotation" - John Smith}

%----------------------------------------------------------------

\begin{document}

\makecvtitle % Print the CV title

%----------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------

\section{Education}

\cventry{2014--2016}{Ph.D. in Computer Science}{Stanford University}{Stanford, CA}{}{
\begin{itemize}
\item{Advised by Professor Gill Bejerano}
\item{Thesis: \emph{Exploring the Genomic Landscape of Human Disease}}
\end{itemize}}
\cventry{2010--2014}{M.S. in Computer Science}{Stanford University}{Stanford, CA}{}{}
\cventry{2006--2010}{B.S. \emph{summa cum laude} in Computer Science}{University of Notre Dame}{}{Notre Dame, IN}{\begin{itemize}
\item{GPA 3.95 / 4.0 (Major 4.0 / 4.0)}\end{itemize}}  % Arguments not required can be left empty


%----------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------
\section{Awards}

\cventry{2013 -- 2016}{SIGF Affymetrix Bio-X Fellowhip}{Stanford University}{}{}{\begin{itemize}
\item{20 awarded across all graduate schools}
\end{itemize}}

\cventry{2010 -- 2013}{Graduate Research Fellowship}{National Science Foundation}{}{}{}

\cventry{2010}{Top Gun Award}{University of Notre Dame}{}{}{\begin{itemize}
\item{Awarded to the senior student-athlete with the
highest GPA}
\end{itemize}}

\cventry{2010}{Outstanding Computer Science Senior Award}{University of Notre Dame}{}{}{\begin{itemize}
\item{Awarded to 2 computer science students}
\end{itemize}}

\cventry{2010}{Reverend Thomas A. Steiner Prize}{University of Notre Dame}{}{}{\begin{itemize}
\item{Awarded to 6 engineering students}
\end{itemize}}

\cventry{2006}{Fourth Place in Teams Award}{Intel International Science \& Engineering Fair}{}{}{}

%----------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------

\section{Work Experience}


\cventry{2017 -- Present}{Head of Informatics}{Circuit Therapeutics}{Menlo Park CA}{}{\begin{itemize}
\item{Delivered gene lists from which many validated targets were selected and licensed to pharmaceutical partners}
\item{Contributed to the gene therapy program by designing a promoter that could be easily packaged in a virus and targeted a specific population of neurons}
\item{Managed a team of one full-time bioinformatics engineer, two remote system administrators, and one machine learning consultant} 
\end{itemize}}

\cventry{2016 -- 2017}{Computational Scientist}{Circuit Therapeutics}{Menlo Park CA}{}{\begin{itemize}
\item{Implemented a single-cell RNA-seq (scRNA-seq) pipeline for processing SMART-seq, DROP-seq, and 10X Chromium libraries}
\item{Addressed the problem of 3' bias in scRNA-seq technologies, which enabled measuring previously missing genes and intergrating samples from different technologies}
\end{itemize}}

\cventry{Fall 2011, Winter 2013}{Teaching Assistant}{Stanford University}{Stanford, CA}{}{Taught review sessions, held office hours, wrote and graded homework assignments, and designed final projects for \emph{Computational Tour of the Human Genome}, a 50 student graduate-level course on current topics in human genomics.}

\cventry{Fall 2009}{Teaching Assistant}{University of Notre Dame}{Notre Dame, IN}{}{Led laboratory sessions, held office hours, and graded projects for \emph{Fundamentals of Computing}, a 30 student undergraduate introduction to programming course.}

\cventry{Summer 2009}{Bing Program Manager Intern}{Microsoft}{Redmond, WA}{}{\begin{itemize}
\item{Managed an international team of developers to build a debugger for Bing's back-end}
\item{Integrated a debugger into pre-existing tools to increase its visibility}
\item{Extracted Bing usage statistics and identified key markets for growth}
\end{itemize}}

%----------------------------------------------------------------
%	RESEARCH EXPERIENCE SECTION
%----------------------------------------------------------------

\section{Research Experience}

\cventry{2010 -- 2016}{Research Assistant}{Bejerano Lab}{Stanford, CA}{}{\begin{itemize}
\item{Used ChIP-seq, ATAC-seq, RNA-seq, and microarray experiments to link \emph{cis}-regulation in the developing neocortex to evolution and autism (jointly mentored by Sue McConnell)}
\item{Enabled non-coding disease-associated mutations from humans to be studied in zebrafish by finding remote homologies (collaboration with the Mourrain Lab)}
\end{itemize}}

\cventry{2008 -- 2010}{Research Assistant}{DIAL Laboratory}{Notre Dame, IN}{}{\begin{itemize}
\item{Conceived an alternative to Google's MapReduce framework for processing large data sets in a mobile environment}
\item{Using patient data and genetic similarities, constructed disease interaction networks to predict unknown disease interactions}
\item{Investigated improving classifier performance on class-imbalanced data sets}
\end{itemize}}

%----------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------

\section{Publications}

\cventry{2018}{{\normalfont Hanson Ho, Matt De Both, Ashley Siniard, Sasha Sharma, \textbf{James H Notwell}, Michelle Wallace, Dino P Leone, Amy Nguyen, Eric Zhao, Hannah Lee, Daniel Zwilling, Kimberly Thompson, Steven P Braithwaite, Matthew J Huentelman, Thomas Portmann. A Guide To Single-Cell Transcriptomics In Adult Rodent Brain: The Medium Spiny Neuron Transcriptome Revisited. \emph{Frontiers in Cellular Neuroscience}}}{}{}{}{}

\cventry{2018}{{\normalfont Romain Madelaine*, \textbf{James H Notwell}*, Gemini Skariah, Caroline Halluin, Charles C Chen, Gill Bejerano, Philippe Mourrain. A Screen for Deeply Conserved Non-Coding GWAS SNPs Uncovers a MIR-9-2 Functional Mutation Associated to Retinal Vasculature Defects in Human. \emph{Nucleic Acids Research} (*Equal contribution)}}{}{}{}{}

\cventry{2017}{{\normalfont Romain Madelaine, Steven A Sloan, Nina Huber, \textbf{James H Notwell}, Louis C Leung, Gemini Skariah, Caroline Halluin, Sergiu P Pasca, Gill Bejerano, Mark A Krasnow, Ben A Barres, Philippe Mourrain. MicroRNA-9 Couples Brain Neurogenesis and Angiogenesis. \emph{Cell Reports}}}{}{}{}{}

\cventry{2016}{{\normalfont \textbf{James H Notwell}, Whitney E Heavner, Siavash Fazel Darbandi, Sol Katzman, William L McKenna, Christian F Ortiz-Londono, David Tastad, Matthew J Eckler, John LR Rubenstein, Susan K McConnell, Bin Chen, Gill Bejerano. TBR1 Regulates Autism Risk Genes in the Developing Neocortex. \emph{Genome Research}}}{}{}{}{}

\cventry{2015}{{\normalfont \textbf{James H Notwell}, Tisha Chung, Whitney Heavner, Gill Bejerano. A Family of Transposable Elements Co-opted into Developmental Enhancers in the Mouse Neocortex. \emph{Nature Communications}}}{}{}{}{}

\cventry{2013}{{\normalfont Aaron M Wenger*, Shoa L Clarke*, \textbf{James H Notwell}*, Tisha Chung, Geetu Tuteja, Harendra Guturu, Bruce T Schaar, Gill Bejerano. The Enhancer Landscape During Early Neocortical Development Reveals Patterns of Dense Regulation and Co-option. \emph{PLoS Genetics} (*Equal contribution)}}{}{}{}{\textbf{Nature Genetics research highlight.}}

\cventry{2013}{{\normalfont Michael Hiller, Saatvik Agarwal, \textbf{James H Notwell}, Ravi Parikh, Harendra Guturu, Aaron M Wenger, Gill Bejerano. Computational Methods to Detect Conserved Non-genic Elements in Phylogenetically Isolated Genomes: Application to Zebrafish. \emph{Nucleic Acids Research}}}{}{}{}{}

\cventry{2009}{{\normalfont Sean McRoskey*, \textbf{James H Notwell}*, Nitesh V. Chawla, Christian Poellabauer. Mining in a Mobile Environment. \emph{International Workshop on Knowledge Discovery from Sensor Data (SensorKDD)}}}{}{}{}{\textbf{Best student paper award.}}

%----------------------------------------------------------------
%	COVER LETTER
%----------------------------------------------------------------

% To remove the cover letter, comment out this entire block

%\clearpage

%\recipient{HR Department}{Corporation\\123 Pleasant Lane\\12345 City, State} % Letter recipient
%\date{\today} % Letter date
%\opening{Dear Sir or Madam,} % Opening greeting
%\closing{Sincerely yours,} % Closing phrase
%\enclosure[Attached]{curriculum vit\ae{}} % List of enclosed documents

%\makelettertitle % Print letter title

%\lipsum[1-3] % Dummy text

%\makeletterclosing % Print letter signature

%----------------------------------------------------------------

\end{document}



